Cosmic web correlations with the shape, spin and peculiar velocties of dark matter halos

### 2014-02-04 paper/main.tex
section numerical experiments

@@

@@

>>>>

\section{Our Numerical Experiments}
In this paper we use the data and the methods described above to
perform three diferent kinds of measurements.

\subsection{Preferential Alignment}

The first measurement is a rough approximation to find out along which
axes are halos aligned. We call this Preferential Alignment (PA).

We use the fact that for a given vector under study $\hat{a}$ and the
tree eigenvectors the following identity holds

\begin{equation}
(\hat{s}\cdot\hat{e}_1)^2 +(\hat{s}\cdot\hat{e}_2)^2 +(\hat{s}\cdot\hat{e}_3)^2 =1.
\end{equation}
%
Using this we know that all halos can be splitted into three groups:

\begin{enumerate}
\item Halos with $(\hat{s}\cdot\hat{e}_1)^2> (\hat{s}\cdot\hat{e}_2)^2$
  and $(\hat{s}\cdot\hat{e}_1)^2> (\hat{s}\cdot\hat{e}_2)$, which can
  be considered to aligned mostly along $\hat{e}_1$.
\item Halos with $(\hat{s}\cdot\hat{e}_2)^2> (\hat{s}\cdot\hat{e}_2)^2$
  and $(\hat{s}\cdot\hat{e}_2)^2> (\hat{s}\cdot\hat{e}_3)^2$, which can
  be considered to aligned mostly along $\hat{e}_2$.
\item Halos with $(\hat{s}\cdot\hat{e}_3)^2> (\hat{s}\cdot\hat{e}_1)^2$
  and $(\hat{s}\cdot\hat{e}_3)^2> (\hat{s}\cdot\hat{e}_1)^2$, which can
  be considered to aligned mostly along $\hat{e}_2$.
\end{enumerate}

If the halo population does not show any preferential alignment, then
all the halos must be evenly distributed along these three
populations. On the contrary, if there is more than one third of the
halo population in one of these sets, then we can talk about a
preferential alignment along one of the axis. However, this statistic 
does not give a precise answer on the degree of the alignment

\subsection{Average Alignment Angle}

We emphasize that all the quantities that we compute in this paper are
independent of any threshold on the eigenvalues that could be used to make a web
clasification into web types. Instead, we focus on the alignments with
respect to the eigenvectors regardless of the web type. In this
context we recall that the eigenvector $\hat{e}_1$ is vector
perpendicular to the plane defining a sheet and also a filamente and
that $\hat{e}_3$ is the vector that marks the direction of a filament
and lies on the plane of a sheet. Therefore we focus on quantifying
the degree of alignment along these two eigenvectors.

This experiment complements the results obtained by the PA satistic by
computing the average and standard deviation of
$\vert\langle\hat{s}\cdot\hat{e}_1\rangle\vert$ and
$\vert\langle\hat{s}\cdot\hat{e}_3\rangle\vert$.  We perform this
tests in differet populations split into different mass bins
logarithmically spaced between $1\times 10^{9}$\hMsun and
$1\times10^{14}$\hMsun.

In a separate test we make the same measurements but this time
splitting the halo sample by other properties such as:
circularity, concentration, local matter density, spin and
triaxiality. In this case we take the upper and lower $30\%$ of the
halos according to each property and measure the strenght of the
alignment by the average value of
$\vert\langle\hat{s}\cdot\hat{e}_1\rangle\vert$ and
$\vert\langle\hat{s}\cdot\hat{e}_3\rangle\vert$.

@@

\subsection{Preferential Alignment}

@@

Figure \ref{fig:preferential} presents all the results for the
preferential alignment (PA).
